\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\hypertarget{sean-mccabe}{%
\section{Sean McCabe}\label{sean-mccabe}}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Long Beach, CA / sean@ulation.com / https://ulation.com / 310.986.2231

\hypertarget{objective}{%
\subsection{Objective:}\label{objective}}

Systems Engineer focusing on DevOps methodologies and collaborating with
engineering teams working to architect solutions, eliminate technical
debt, and implement automation.

\hypertarget{professional-experience}{%
\subsection{Professional Experience:}\label{professional-experience}}

\hypertarget{tribune-interactive-formally-tronc-tribune-publishing}{%
\subsubsection{Tribune Interactive (formally Tronc \& Tribune
Publishing)}\label{tribune-interactive-formally-tronc-tribune-publishing}}

\emph{August 2017 -- April 2018} \emph{DevOps Engineer} Digital and
print publisher for 10 major papers including The Los Angeles Time and
The Chicago Tribune.

\begin{itemize}
\tightlist
\item
  Work with developers to streamline CI/CD for application deployments.
\item
  Provision, monitor, and maintain cloud infrastructure on AWS,
  including EC2, RDS, Lambda, Cloudwatch, and more.
\item
  Manage updates and configurations for dozens of sites.
\item
  Review AWS IAM policies and permissions, perform security audit, and
  implement best-practice security configurations
\item
  Use Saltstack and other configuration management platforms to deploy
  states and updates to servers and applications.
\item
  Guide development team with solutions and platforms for frameworks and
  upgrades
\item
  Collaborate with NPE's (Newsroom Product Engineers) to create and
  deploy tools in the newsrooms for journalism staff.
\item
  Gather project requirements from product owners and architect
  proof-of-concept solutions for internal technology projects
\item
  Create and maintain Jenkins build pipelines.
\end{itemize}

\hypertarget{the-black-tux---santa-monica}{%
\subsubsection{The Black Tux - Santa
Monica}\label{the-black-tux---santa-monica}}

\emph{November 2016 -- July 2017} \emph{DevOps Engineer}

The Black Tux is an online service for renting a tuxedo or suit, using
expertise and technology to provide an amazing and seamless experience
to the customer.

\begin{itemize}
\tightlist
\item
  Rearchitect staging and production environments to be fully container
  based.
\item
  Create Terraform Modules and Scripts to deploy AWS environments.
\item
  Work with development team to deploy daily builds in blue, green
  deployments.
\item
  Help convert applications to serverless infrastructure in Lambda and
  S3 endpoints through Serverless and CodePipeline.
\item
  Build Docker containers for development environments.
\item
  Create documentation on common procedures.
\item
  Troubleshoot and update SQL databases.
\item
  CDN and DNS management with Akamai and Cloudfront.
\item
  Support Django application and builds and deployments.
\item
  Centralize logging with ELK.
\item
  Redefined CI/CD pipeline using AWS suite of tools.
\item
  Review and analyze billing and costs to maximize savings in AWS.
\end{itemize}

\hypertarget{daqri-downtown-los-angeles}{%
\subsubsection{DAQRI, Downtown Los
Angeles}\label{daqri-downtown-los-angeles}}

\emph{November2014 - October2016}\\
\emph{Systems Administrator / Cloud Engineer}

Startup geared to releasing AR devices and applications.

\textbf{DevOps:}

\begin{itemize}
\tightlist
\item
  Manage production servers used for helmets, maintaining 99\% uptime,
  ensuring a secure environment and responding to immediate issues.
\item
  Migrate local infrastructure into AWS; Perform AWS Administration,
  with EC2, S3, Lambda, VPC, IAM, RDS, R53 and more.
\item
  Deploy OpsWorks website stacks.
\item
  Manage distributed cloud-based and local systems using Terraform;
  write and deploy Docker containers via Rancher.
\item
  Configure, deploy, and automate Jenkins CI Build Master and slaves.
\item
  Manage and deploy NGINX and Apache websites and proxies with SSL.
\item
  Manage version control repositories on GitHub and BitBucket, team's
  usage strategy, and reduce costs
\item
  Manage local and remote VMware infrastructure and deploy physical and
  virtual servers and networks in remote offices.
\item
  Develop backup and recovery strategies for local and cloud
  environments; ensure availability and uptime for critical systems.
\item
  Architect, manage, and support migration of corporate infrastructure
  from Office 365 to Google Apps.
\item
  Help plan and coordinate office expansion to an additional floor,
  including office moves and network configuration.
\item
  Setup proactive Nagios monitoring and alerts for local systems and
  applications; evaluate ELK stack (Elasticsearch, Logstash, and Kibana)
  as an alternate or supplementary logging solution.
\item
  Manage Solidworks EPDM and MSSQL servers with replicas; manage flex
  license servers locally and in AWS.
\end{itemize}

\textbf{Training and Leadership:}

\begin{itemize}
\tightlist
\item
  Work with AWS rep to create a plan to save over \$110K/yr in Reserved
  Instances.
\item
  Coordinate move of services to AWS Lambda, saving \$20K a year, no
  longer needing c4.large instances to do compute.
\item
  Save the company over \$100K in software and licensing by negotiating
  and maintaining corporate contracts with vendors.
\item
  Proactively research and recommend new technologies and systems for
  short-term and long-term solutions to address company's business
  needs, and assist with driving software and service purchasing
  strategy.
\item
  Create training and reference documentation on systems installation,
  operations and configuration, and procedures for technical and
  non-technical staff.
\item
  Implement and train staff on good security practices. Offering
  phishing training and safe password management systems.
\item
  Mentor, train, and lead team on technical projects, systems
  administration best practices, VMware and AWS tools.
\item
  Manage projects and operations using Wrike, Jira, and Confluence;
  promote project management and collaboration amongst the IT team;
  create documentation for all current working systems.
\end{itemize}

\hypertarget{raytheon-secure-information-systems-contract-el-segundo}{%
\subsubsection{Raytheon Secure Information Systems, Contract, El
Segundo}\label{raytheon-secure-information-systems-contract-el-segundo}}

\emph{March 2014 - September2015} \emph{Systems Administrator}

Move and migrate large-scale dual production, Secret and Local,
environments from one location to another. Architect and integrate
applications into hosted services under mother company. Working with DOD
incidents and secrecy.

\textbf{Key Projects:}

\begin{itemize}
\tightlist
\item
  Coordinate large-scale move of critical production environment with
  over 100 servers from offsite satellite office into the main office
  campus, including: architecting migration plan, from shutdown and
  move, to re-rack and reconfiguration, power-on, and testing; creating
  risk assessment and failover plans for server move process; and
  working with application owners to create application migration plan.
\item
  Implement SCCM patch management and event logging server.
\item
  Re-establish and manage backup procedure and document backup processes
  and policies for auditing purposes.
\item
  Create and maintain infrastructure documentation, including server,
  VM, and printer configurations.
\end{itemize}

\textbf{Server Administration:}

\begin{itemize}
\tightlist
\item
  Lead resource for managing Windows 2003/2008/Ubuntu server
  infrastructure
\item
  Manage several networks, including air-gapped \& closed networks.
\item
  Manage \& troubleshoot VMware vCenter and vmdx files on blade servers.
\item
  Troubleshoot and replace parts on EMC SAN systems and HP ProLiant
  systems from G2 to current.
\item
  Train junior staff on workings of environment and new technologies.
\item
  Work in PowerShell and create scripts to automate tasks; evaluate and
  recommend automation tools for use by the team
\item
  Work with development team to support and document engineering
  software and requirements, including MKS, GIT, VSS, GreenHills,
  Mentor, ProcessMax, Doors, and more.
\end{itemize}

\end{document}
